\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape RUSHIL GUPTA} \\ \vspace{2pt}
    \small 8375911611 $|$ \href{mailto:rushilgupta4@gmail.com}{\underline{rushilgupta4@gmail.com}} $|$ \href{https://linkedin.com/in/rushilgupta4}{\underline{linkedin.com/in/rushilgupta4}} $|$ \href{https://github.com/RushilGupta4}{\underline{github.com/RushilGupta4}} \\
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ashoka University}{}
      {B.Sc (Hons) in Mathematics and Computer Science with Research; CGPA: 3.84/4}{Expected 2027}
    \resumeSubheading
      {Pathways School Noida}{}
      {Class XII, International Baccalaureate (IB); Score: 92\%}{2023}
  \resumeSubHeadingListEnd

%-----------RELEVANT COURSEWORK-----------
\section{Relevant Coursework}\vspace{-10pt}
\begin{multicols}{2}
\begin{itemize}[leftmargin=*, noitemsep, topsep=-10pt]
    \item Real Analysis
    \item Introduction to Quantitative Finance
    \item Introduction to Machine Learning
    \item Reinforcement Learning
\end{itemize}
\end{multicols}

%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Researcher}{Dec 2024 -- Present}
      {Safexpress Centre for Data, Learning and Decision Sciences}{}
      \resumeItemListStart
        \resumeItem{Developing scalable agent-based epidemiological models for disease spread across Indian cities.}
        \resumeItem{Exploring diffusion models to enhance rare event sampling techniques.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Intern}{Feb 2024 -- Dec 2024}
      {KOITA Centre for Digital Health Ashoka}{}
      \resumeItemListStart
        \resumeItem{Developed infrastructure for a cohort study integrating data steams including GOQii, a custom mobile app, etc.}
        \resumeItem{Worked on an LLM solution to automate informed consent, leveraging agentic models for improved performance.}
        \resumeItem{Researched early-stage ICU outcome prediction using ML, achieving a 10\% improvement in accuracy.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
    \resumeSubheading
      {Platform Teams Intern}{Nov 2024 -- Feb 2025}
      {SARVAM AI}{}
      \resumeItemListStart
        \resumeItem{Designed a robust versioning system for voice agents enabling incremental updates and seamless deployment.}
        \resumeItem{Implemented the first unit and integration tests for backend microservices, improving API reliability}
      \resumeItemListEnd
      \resumeSubHeadingListEnd

%-----------POSITIONS OF RESPONSIBILITY-----------
\section{Positions of Responsibility}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Head of Events}{Sep 2023 -- Present}
      {Ashoka Computer Science Society}{}
      \resumeItemListStart
        \resumeItem{Led a team of 20 members in planning and executing events, including talks, workshops, and academic events.}
        \resumeItem{Initiated Leetcode Saturdays - weekly competitive programming sessions for students to solve problems together.}
      \resumeItemListEnd

    \resumeSubheading
      {Co-Founder and Head of Events \& Logistics}{Mar 2024 -- Dec 2024}
      {Ashoka Health Research Club}{}
      \resumeItemListStart
        \resumeItem{Ideated and co-founded the club, being involved in the selection process of the core and events team.}
        \resumeItem{Executed a 5-day launch event series in collaboration with 4 academic societies to promote health research.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Ensemble model with inherently good quality data improves early mortality prediction in ICUs}}{Jan 2025}
      {Critical Care Medicine}{}
      \resumeItemListStart
        \resumeItem{Developed a novel ensemble model and methods to identify high-quality subsets of ICU data, significantly enhancing early mortality prediction accuracy in ICU patients.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item{
      \textbf{Languages}{: Python, JavaScript, Julia, Scala, OCaml, HTML, CSS} \\
      \textbf{Frameworks}{: PyTorch, FastAPI, Django, Pandas, NextJs, React Native, LangChain} \\
      \textbf{Tools}{: Docker, Git, CI/CD, AWS, GCP, Firebase, PostgreSQL, Redis} \\
    }
 \end{itemize}

\end{document}